\newpage
\section{APPLICATIONS}


		\hspace{5mm}Tetris was originally inspired by a puzzle game called "pentominoes," in which different wooden shapes made of five equal squares are assembled in a box. Hence, Tetris is also a puzzle in itself and thus a “mind” game. Although, video games are often dismissed as unsophisticated or the domain of couch potatoes, but many common elements of these simulated worlds can provide tangible benefits in real life. Benefits of Tetris for both children and adults include:
		\begin{itemize}
			\item Healthy Brain Simulation
			\item Development of Problem Solving Skills
			\item Stress Relief
		\end{itemize}
		
		\hspace{5mm}Taking these benefits into account, application of Tetris are discussed below:
		
			\begin{enumerate}
				\item \textbf{Problem Solving:} As already mentioned above, Tetris is a puzzle game and thus, is a tool to develop problem solving skills. Placing each block requires a strategy so
				to get that neat high score everyone craves for. This, in turns develops a habit of searching of the best route for the required outcome.
				\item \textbf{Quick Decision Making:} Tetris does not only require a gamer to develop a strategy but it also requires them to make a decision to take a certain strategy in a
				quick manner. There is so little time between the clearing of a line and the falling of
				the next block that the gamer must choose an optimum decision quickly.
				\item \textbf{Mental Health:}With something as concerning as mental health, it is only right to
				search for a remedy to it that boosts morale and mood. Tetris, and video games, in
				general, are a great tool that can be very helpful.
				\item \textbf{Learning:}Although video games are portrayed as something that is an obstruction
				for learning, in truth, the portrayal is anything but far from truth. Tetris can be a great tool for learning as one is required to use their memory, spatial intelligence, problem solving, decision making, etc.
				\item \textbf{Balancing Time and Priority:}Tetris can be a great teacher if you’re having difficulty prioritizing. To keep up with the game, you must change your priorities
				very quickly. You can apply this pattern in the real world when you encounter situations that disturb your routine and require you to switch tasks.
			\end{enumerate}
		