\newpage
\section{OBJECTIVES}
The objectives of building this game in C++ are listed below:


\begin{enumerate}
\item \textbf{Use Object-Oriented Programming (OOP):}
	\begin{itemize}
		\item Create classes for Tetrominoes, game board, and game logic.
		\item Organize code for easy maintenance and flexibility.
	\end{itemize}
	
\item \textbf{Explore C++ Features:}
\begin{itemize}
	\item Manage game data efficiently using arrays and vectors.
	\item Handle resources smartly to optimize performance.
\end{itemize}

\item \textbf{Graphics with SFML:}
\begin{itemize}
	\item Use SFML to draw Tetrominoes, game board, and animations.
	\item Respond to player input using SFML's event system.
\end{itemize}

\item \textbf{Reusable Code:}
\begin{itemize}
	\item Create header files for sharing code across the game.
\end{itemize}

\item \textbf{Implement Game Mechanics:}
\begin{itemize}
	\item Make Tetrominoes rotate, move, and detect collisions.
	\item Create a scoring system and difficulty levels.Create a scoring system and difficulty levels.Create a scoring system and difficulty levels.
\end{itemize}

\item \textbf{Add Sound Effects and Music:}
\begin{itemize}
	\item Integrate audio using SFML for a better gaming experience.
\end{itemize}

\item \textbf{Test and Debug:}
\begin{itemize}
	\item Thoroughly test the game to fix any issues.
	\item Use logs and debugging tools for troubleshooting.
\end{itemize}

\item \textbf{Team Collaboration:}
\begin{itemize}
	\item Communicate well within the team.
	\item Use Git for version control and collaboration.
\end{itemize}
\end{enumerate}